\section{Full Reproducibility Script (All Six Experiments)}

This appendix documents a single-command procedure that reproduces the full six-experiment evaluation pipeline used in this study, including policy runtime comparisons, storage-mode comparisons, latency summaries, unauthorized-access checks, policy-version traceability checks, and tamper-evidence validation.

\subsection{Script Location and Purpose}

\begin{itemize}
  \item Script: \texttt{experiment/scripts/run\_full\_six\_experiments.sh}
  \item Purpose: Execute all experiment modes end-to-end and generate timestamped outputs in \texttt{experiment/raw/}.
  \item The script orchestrates:
    \begin{enumerate}
      \item matrix runs across runtime/storage configurations,
      \item final verification capture,
      \item consolidated latency summary generation,
      \item automated tamper journey (\texttt{UPDATE} and \texttt{DELETE} in DB followed by verification checks).
    \end{enumerate}
\end{itemize}

\subsection{Preconditions}

Before running the script, the following must be available:
\begin{itemize}
  \item PostgreSQL with the \texttt{governdata} schema available.
  \item Governance service dependencies for real mode.
  \item OPA reachable at \texttt{localhost:8181} for OPA runs.
  \item Hyperledger Fabric and governance chaincode running for blockchain/hybrid modes.
  \item Valid tenant API key (environment variable \texttt{GOVERNANCE\_API\_KEY}).
  \item Local tools: \texttt{bash}, \texttt{curl}, \texttt{python3}, \texttt{psql}.
\end{itemize}

\subsection{Execution}

\begin{verbatim}
chmod +x experiment/scripts/run_full_six_experiments.sh
./experiment/scripts/run_full_six_experiments.sh
\end{verbatim}

Optional environment variables:
\begin{verbatim}
export GOVERNANCE_API_KEY=<your-key>
export GOV_BASE_URL=http://localhost:8080
export GOV_DB_NAME=governdata
# Optional alternative:
# export GOV_DB_URL=postgresql://user:pass@localhost:5432/governdata
\end{verbatim}

\subsection{What the Script Produces}

Each run writes timestamped outputs under \texttt{experiment/raw/}:
\begin{itemize}
  \item \texttt{full\_experiment\_<label>\_<timestamp>.json} \\
  Per-run capture containing benchmark, client latency (min/max/avg/p95), policy-version probe, unauthorized scenario, and ingest/verify checks.
  \item \texttt{matrix\_summary\_<timestamp>.json} \\
  Aggregated latency table for the latest matrix labels.
  \item \texttt{tamper\_journey\_<timestamp>.json} \\
  Ordered evidence for ingest $\rightarrow$ verify $\rightarrow$ DB update $\rightarrow$ verify $\rightarrow$ DB delete $\rightarrow$ verify.
\end{itemize}

\subsection{Mapping to the Six Experiments}

\begin{enumerate}
  \item \textbf{Policy Engine Comparison}: reproduced by JSON vs OPA matrix runs and client-latency summaries.
  \item \textbf{DB vs Blockchain Integrity}: reproduced by storage-mode runs and verify outcomes.
  \item \textbf{Hybrid Audit Model}: reproduced in BOTH mode with chain anchoring evidence.
  \item \textbf{Policy Version Traceability}: reproduced by repeated authorization probe with version metadata capture.
  \item \textbf{Unauthorized Access Handling}: reproduced by no-consent scenario and expected/actual decision comparison.
  \item \textbf{Latency Overhead}: reproduced from post-warmup latency summaries and matrix aggregation.
\end{enumerate}

\subsection{Automated Tamper Sequence}

The script performs the tamper steps automatically:
\begin{enumerate}
  \item Ingest external audit event.
  \item Verify baseline status.
  \item Execute SQL \texttt{UPDATE} against \texttt{external\_audit\_events}.
  \item Verify mismatch status.
  \item Execute SQL \texttt{DELETE} against \texttt{external\_audit\_events}.
  \item Verify chain-only recovery status (in real chain mode).
\end{enumerate}

\subsection{Defense-Ready Reproducibility Statement}

\textit{All six experiments are reproducible via one orchestrator script. The procedure generates timestamped raw outputs and summarized metrics, and includes an automated tamper-evidence sequence to demonstrate integrity behavior under adversarial database modification and deletion.}

